Background Music Will not Significantly Distract Attention

### 2021-04-25 Output/paper/paper.Rmd
update paper

anova (nullmodel1, nullmodel2, nullmodel3)%>%
   kbl(caption = 'The result of comparing model by ANOVA',
      align = "cccc") %>%
  kable_styling(latex_options = "hold_position")

>>>>

round(anova (nullmodel1, nullmodel2, nullmodel3),2)%>%
   kbl(caption = 'The result of comparing model by ANOVA',
      align = "cccc") %>%
  kable_styling(latex_options = "hold_position")
